|

### 2024-03-26 index.qmd
update author list

- **Publicly Available Code**: Future updates will include ready-to-use code examples for your research and educational needs. See some initial examples [here](https://opendevsci.github.io/LongDev-ABCD/examples/examples.html) or in the `examples` folder of our [GitHub repository](https://github.com/OpenDevSci/LongDev-ABCD)
- **Open Source Collaboration**: Engage with our community to contribute, learn, and share insights on longitudinal data analysis.
- **Educational Resource**: Gain comprehensive knowledge in using GitHub, R, RMarkdown/Quarto, and various longitudinal analysis methods with our guidance.

@@

- **[Code Examples](https://github.com/OpenDevSci/LongDev-ABCD)**: Discover a variety of analysis examples to guide your research.
- **[Documentation](https://github.com/orgs/OpenDevSci/projects/13)**: Get detailed insights into our project's progress, tasks, and timelines.
- **[Community Discussion Forum](https://github.com/orgs/OpenDevSci/discussions)**: Connect with fellow researchers and enthusiasts in our dedicated forum.

@@

**Together, let's advance the field of data analysis.**

>>>>

- **Publicly Available Code**: Future updates will include ready-to-use code examples for your research and educational needs. See some initial examples [here](https://opendevsci.github.io/LongDev-ABCD/examples/examples.html) or in the `examples` folder of our [GitHub repository](https://github.com/OpenDevSci/LongDev-ABCD)
- **Open Source Collaboration**: Engage with our community to contribute, learn, and share insights on longitudinal data analysis.
- **Educational Resource**: Gain comprehensive knowledge in using GitHub, R, RMarkdown/Quarto, and various longitudinal analysis methods.

@@

- **[Code Examples](https://github.com/OpenDevSci/LongDev-ABCD)**: Discover a variety of analysis examples to guide your research.
- **[Documentation](https://github.com/orgs/OpenDevSci/projects/13)**: Get detailed insights into our project's progress, tasks, and timelines.
- **[Community Discussion Forum](https://github.com/orgs/OpenDevSci/discussions)**: Connect with fellow researchers and enthusiasts .

@@

### 2024-03-26 manuscript/manuscript.qmd
update author list

---
title: |
  Longitudinal Analysis Manuscript: Working Draft
subtitle: Longitudinal Analysis using data from the ABCD© Study
short-title: Longitudinal Analysis
code-repo: "Access the code, data, and analysis at <http://swhawes.github.io/test/>"
number-sections: true
number-depth: 3
correspondence-prefix: "Correspondence concerning this article should be addressed to"
author:
  - name: Samuel Hawes
    email: shawes@fiu.edu
    title: Associate Research Professor
    affiliations:
      #- id: ds9
        name: Florida International University
        department: Center for Children & Families
        address: 11200 SW 8th St, AHC-IV
        city: Miami
        region: FL
        country: USA
        postal-code: 33199
    attributes:
      corresponding: true
  - name: Andrew K. Littlefield
    email: andrew.littlefield@ttu.edu
    affiliations:
      #- id: ds9
        name: Texas Tech University
        department: Psychological Sciences
        city: Lubbock
        region: TX
        country: USA
  - name: Daniel A. Lopez
    email: Daniel_Lopez2@URMC.Rochester.edu
    affiliations:
      #- id: terok
        name: University of Rochester Medical Center
        department: Department of Public Health
        city: Rochester
        region: NY
        country: USA
      #- ref: ds9
  - name: Kenneth J. Sher
    email: SherK@missouri.edu
    affiliations:
      #- id: ds9
        name: University of Missouri
        department: Psychological Sciences
        city: Columbia
        region: MO
        country: USA
  - name: Erin L. Thompson
    email: erthomps@fiu.edu
    affiliations:
      #- id: terok
        name: Florida International University
        department: Center for Children and Families
        city: Miami
        region: FL
        country: USA
  - name: Raul Gonzalez
    email: gonzara@fiu.edu
    affiliations:
      #- id: ds9
        name: Florida International University
        department: Center for Children and Families
        city: Miami
        region: FL
        country: USA
  - name: Additional Co-authors
    email: xxxxx@fiu.edu
    affiliations:
      #- id: terok
        name: xxxxxx University
        department: xxxxxx Dept
        city: xxxx
        region: xxxxx
        country: xxxxx
  - name: Wesley K. Thompson
    email: wes.stat@gmail.com
    affiliations:
      #- id: terok
        name: Laureate Institute for Brain Research
        department: Center for Population Neuroscience and Genetics
        city: Tulsa
        region: OK
        country: USA

>>>>

title: |
  Longitudinal Analysis Manuscript: Working Draft
subtitle: Longitudinal Analysis using data from the ABCD© Study
short-title: Longitudinal Analysis
code-repo: "Access the code, data, and analysis at <http://swhawes.github.io/test/>"
number-sections: true
number-depth: 3
correspondence-prefix: "Correspondence concerning this article should be addressed to"
author:
- name: Samuel W. Hawes
  email: shawes@fiu.edu
  affiliations:
    name: Florida International University
    department: Center for Children & Families
    city: Miami
    region: FL
    country: United States
- name: Andrew K. Littlefield
  email: andrew.littlefield@ttu.edu
  affiliations:
    name: Texas Tech University
    department: Psychological Sciences
    city: Lubbock
    region: TX
    country: United States
- name: Daniel A. Lopez
  email: lopdanie@ohsu.edu
  affiliations:
    name: Oregon Health & Science University
    department: Department of Psychiatry
    city: Portland
    region: OR
    country: United States
- name: Kenneth J. Sher
  email: SherK@missouri.edu
  affiliations:
    name: University of Missouri
    department: Psychological Sciences
    city: Columbia
    region: MO
    country: United States
- name: Erin L. Thompson
  email: erthomps@fiu.edu
  affiliations:
    name: Florida International University
    department: Center for Children & Families
    city: Miami
    region: FL
    country: United States
- name: Raul Gonzalez
  email: gonzara@fiu.edu
  affiliations:
    name: Florida International University
    department: Center for Children & Families
    city: Miami
    region: FL
    country: United States
- name: Laika Aguinaldo
  email: laaguinaldo@health.ucsd.edu
  affiliations:
    name: University of California San Diego
    department: Department of Psychiatry
    city: San Diego
    region: CA
    country: United States
- name: Ashley R. Adams
  email: asadams@fiu.edu
  affiliations:
    name: Florida International University
    department: Center for Children & Families
    city: Miami
    region: FL
    country: United States
- name: Mohammadreza Bayat
  email: mbayat@fiu.edu
  affiliations:
    name: Florida International University
    department: Cognitive Neuorscience
    city: Miami
    region: FL
    country: United States
- name: Amy L. Byrd
  email: byrdal@upmc.edu
  affiliations:
    name: University of Pittsburgh
    department: Department of Psychiatry
    city: Pittsburgh
    region: PA
    country: United States
- name: Luis FS Castro-de-Araujo
  email: Luis.Araujo@vcuhealth.org
  affiliations:
    name: Virginia Commonwealth University
    department: Virginia Institute for Psychiatric and Behavioral Genetics
    city: Richmond
    region: VA
    country: United States
- name: Anthony Dick
  email: adick@fiu.edu
  affiliations:
    name: Florida International University
    department: Cognitive Neuorscience
    city: Miami
    region: FL
    country: United States
- name: Steven F. Heeringa
  email: sheering@umich.edu
  affiliations:
    name: University of Michigan
    department: Institute for Social Research
    city: Ann Arbor
    region: MI
    country: United States
- name: Christine M. Kaiver
  email: ckaiv001@fiu.edu
  affiliations:
    name: Florida International University
    department: Center for Children & Families
    city: Miami
    region: FL
    country: United States
- name: Sarah M. Lehman
  email: slehman@fiu.edu
  affiliations:
    name: Florida International University
    department: Center for Children & Families
    city: Miami
    region: FL
    country: United States
- name: Lin Li
  email: lil033@ucsd.edu
  affiliations:
    name: University of California San Diego
    department: Department of Radiology
    city: San Diego
    region: CA
    country: United States
- name: Janosch Linkersdörfer
  email: jlinkersdoerfer@ucsd.edu
  affiliations:
    name: University of California San Diego
    department: Center for Human Development
    city: San Diego
    region: CA
    country: United States
- name: Thomas J. Maullin-Sapey
  email: Thomas.Maullin-Sapey@bdi.ox.ac.uk
  affiliations:
    name: University of Oxford
    department: Oxford Big Data Institute
    city: Oxford
    region: UK
    country: United Kingdom
- name: Michael C. Neale
  email: Michael.Neale@vcuhealth.org
  affiliations:
    name: Virginia Commonwealth University
    department: Virginia Institute for Psychiatric and Behavioral Genetics
    city: Richmond
    region: VA
    country: United States
- name: Thomas E. Nichols
  email: thomas.nichols@bdi.ox.ac.uk
  affiliations:
    name: University of Oxford
    department: Oxford Big Data Institute
    city: Oxford
    region: UK
    country: United Kingdom
- name: Samantha Perlstein
  email: sperl@sas.upenn.edu
  affiliations:
    name: University of Pennsylvania
    department: Department of Psychology
    city: Philadelphia
    region: PA
    country: United States
- name: Susan F. Tapert
  email: stapert@ucsd.edu
  affiliations:
    name: University of California San Diego
    department: Department of Psychiatry
    city: San Diego
    region: CA
    country: United States
- name: Colin E. Vize
  email: CEV18@pitt.edu
  affiliations:
    name: University of Pittsburgh
    department: Department of Psychology
    city: Pittsburgh
    region: PA
    country: United States
- name: Margot Wagner
  email: mwagner@ucsd.edu
  affiliations:
    name: University of California San Diego
    department: The Institute for Neural Computation
    city: San Diego
    region: CA
    country: United States
- name: Rebecca Waller
  email: rwaller@sas.upenn.edu
  affiliations:
    name: University of Pennsylvania
    department: Department of Psychology
    city: Philadelphia
    region: PA
    country: United States
- name: Wesley K. Thompson
  email: wes.stat@gmail.com
  affiliations:
    name: Laureate Institute for Brain Research
    department: Center for Population Neuroscience and Genetics
    city: Tulsa
    region: OK
    country: United States
